\documentclass[iop,apj]{emulateapj}
\usepackage{amsmath,amssymb,amstext}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
\renewcommand*{\sectionautorefname}{Section}
\usepackage[all]{hypcap} %Links go to figures; breaks on deluxetables (use \capstartfalse \capstarttrue to fix it)
\usepackage[]{algorithm2e}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{float}
\usepackage{graphicx}
\usepackage[ampersand]{easylist}
\usepackage{verbatim}
\usepackage{trimclip}

\begin{document}

\title{[Automatic Identification of Spectral Lines through Spectrum Reconstruction]}
\author{Andr\'es Riveros	$^1$}
\author{Karim Pichara		$^{1,5, 2}$}
\author{Pavlos Protopapas	$^2$}
\author{Diego Mardones		$^3$}
\author{Mauricio Araya		$^4$}
\affil{$^1$ Computer Science Department, Pontif\'icia Universidad Cat\'olica de Chile, Santiago, Chile}
\affil{$^2$ Institute for Applied Computational Science, Harvard University, Cambridge, MA, USA}
\affil{$^3$ Astronomy Department, Universidad de Chile, Santiago, Chile}
\affil{$^4$ Computer Science Department, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso, Chile}
\affil{\altaffilmark{5}Millennium Institute of Astrophysics, Chile}

\begin{abstract}

\begin{comment}
    - Massive Amount of Data
    - Astronomers overloaded
    - What is spectroscopy
    - Need to automatize process
    - Step by step task of astronomer
    - Focus of this work
    - Automatic Proposed Algorithm
    - Detailing Algorithm Operation
    - Reached Results
    - Strengths and limitations
    - Conclusions
\end{comment}


Astronomy is facing new challenges on how to analyze big data and therefore, how to search or predict events/patterns of interest.
New observations in previously unexplored wavelength regions will be available from instruments such as the Atacama Large Millimeter Array (ALMA).
Given this growing amount of high spectral resolution data, any non-automatic analysis would be an effort beyond human's capacity.
Currently, classifying emission lines means to decide if a particular emission line belongs to a specific isotope. 
This classification is mainly done by comparing them with known isotopes emission lines.
An automatic line-classification algorithm would dramatically reduce human efforts to analyze spectral data, allowing astronomers to focus their efforts in deeper analysis.

In this work, we propose an algorithm that uses a sparse model to represent the spectra and automatically classify emission lines.
We use spectral line databases to determine a set of basis vectors that represent the presence of theoretical emission lines.
Then, to classify lines in a given spectrum, the difference between the spectrum and a linear combination of the determined basis vectors is minimized.

The model's output correspond to a probability vector representing the distribution of the prediction over a set of possible isotopes. 
We test our algorithm with experimental data from Splatalogue and simulated data from the ASYDO project.
The results of the analysis show that the algorithm is able to identify emission lines with an accuracy of 90\% when no blending nor hyperfine cases are present.
As wavelength separation decreases (equal or less than $1$ MHz), accuracy goes down to 82\%.

The source code of the algorithm, synthetic data cubes used and list of suggested identifications are publicly available \footnote{https://github.com/ChileanVirtualObservatory/DISPLAY}.

\end{abstract}

\keywords{
    spectral lines: emission lines;
    technique: spectroscopy;
    method: data analysis
    }

\maketitle

\input{include/1_introduction}

\input{include/2_background}

\input{include/3_sota}

\input{include/4_data_origin}

\input{include/5_algorithm}

\input{include/6_results}

\input{include/7_conclusion}

\input{include/8_acknowledgments}

\thispagestyle{empty}

\addcontentsline{toc}{section}{References}
\bibliography{paper-meta}
\bibliographystyle{plainnat}

\end{document}